Verifying Demonstrations

### 2020-04-20 paper/protocol-trusted.tex
Starts splitting protocol into trusted/untrusted
Improves intro to trusted witnesses protocol

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}%
\label{Protocol}

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key%
%, more specifically, an anonymous 
%identity credential that provides unlinkability between contexts but 
%linkability for reuse within the same context
%\sonja{this is actually achieved by our use of prfs for pid and wid,
%not inherent in the credential}
% \footnote{%
%   Given any \ac{CA} that prevents Sybil 
%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
%   be used to make sure that for each identity one-and-only-one
%   cryptographic key is issued.
%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
%   to one's identity.
% }
. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

The core of the \CROCUS protocol consists of generating participation
proofs (joining a protest, participating in witnessing, submitting
proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
verification of that count (in \cref{ProtocolVerification}).

% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
% join, participation, submission (all in in \cref{ProtocolDuring}) and
% verification (in \cref{ProtocolVerification}).

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

After the protest, anyone can count the number of participants (of the protest and the
protocol) and verify anyone else's count given the relevant meta data
(which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

\subsection{Prerequisite: anonymous credentials}%
\label{ProtocolSetup}

>>>>

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The trusted-witnesses protocol}%
\label{trusted-witnesses-protocol}

We now present a protocol for privacy-preserving but verifiable crowd
counts.
This version of the protocol relies on trusted entities to act as witnesses for 
\iac{LP}.

A prerequisite for this protocol is a one-to-one mapping between a persons real 
identity and a certificate (\ie a cryptographic key).
\Cref{ProtocolSetup} covers how Alice can obtain such a certificate.
It is a lighter version than in \cite{SelfCertifiedSybilFreePseudonyms} and not 
the full protocol of \cite{HowToWinTheCloneWars}.

At the core of our construction, witnesses generate participation proofs for 
the protesters (in \cref{ProtocolDuring}), these are essentially augmented 
\acp{LP}\footnote{%
  \Iac{LP} certifies that its owner was at a given location at a given time.
  In \cref{protest-model}, we point out that we also need a cause identifier.
}.
Then whoever wants to verify the participation count, will count and verify 
those participation proofs (in \cref{ProtocolVerification}).

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs of participation to protesters.
  The proofs are constructed such that they are verifiable by third parties.
  The witness must be trusted by the verifier.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

Anyone can be a verifier (we required universal verifiability, 
\cref{desired-properties}).
The verifier defines the protest to be counted by setting the cause, time 
(interval) and location (area), \cf \cref{DefProtest}.
Now the verifier counts all proofs that verify correctly and fulfils the cause, 
time and location criteria.
The verifier can publish, \eg in a news paper, the final count together with 
the cause, time and location and anyone can verify this count (by the same 
procedure).

\subsection{Prerequisite: self-certified, Sybil-free pseudonyms}%
\label{ProtocolSetup}
